TacticToe: Learning the Game of Tactics

### 2018-02-15 tactictoe_jv.tex
Some random grammar edits

\section{Case Study}\todo{comment on the case study}
Since the proofs generated by \tactictoe are meant to be part of a \holfour
development, it interesting to compare their quality with the original human
proofs. The quality of a proof in \holfour can be measured in terms of length,
, readability, maintainability and verification speed. We study these
properties
in three examples taken from our full-scale experiment. The time needed by
\holfour to check a proof is shown in parentheses.

In Example~\ref{ex:cs1}, the uniqueness of the greatest common divisor is
proven. The human developer recognizes that it follows easily from two theorems.
Our prover \tactictoe is not able to find that \texttt{DIVIDES\_ANTISYM} is
necessary directly from the shape of the original theorems so it rewrites the
goal and split the goal into multiple cases until goal obligations are similar
to \texttt{DIVIDES\_ANTISYM} to be predicted. As expected, \tactictoe's proof
also takes much longer to check.

@@

In Example~\ref{ex:cs2}, we try to prove that for any surjective function $f$
from $s$ to $t$, there exists an injective function $g$ from $t$ to $s$ such
that $f\ o\ g$ is the identity function. The human proof is quite complicated.
In
contrast, \tactictoe finds a much smaller proof that expands the
definition of injectivity and surjectivity and calls \metis. However, the
\tactictoe's script does take much longer to check due to the proof search
happening inside
\metis.

@@

In Example~\ref{ex:cs3}, we prove a theorem about lists which is domain where
\tactictoe excels compared to ATPs.
Given two list $l_1$ and $l_2$ where the length of $l_1$ (noted $p$) is less
than a natural
number $n$, the theorem states updating the $n^{th}$
element of the concatenation of $l_1$ and $l_2$ is the same as
updating the $m^{th}$ element of $l_2$ where $m = n - p$. Again,
\tactictoe's proof is
much more readable starting with applying induction on $l$. It solves the base
case of the induction by rewriting and distinguish cases where $n=0$ or $n>0$
in the inductive hypothesis. It finalizes the proof with a short call to \metis
using the definition of
$LUPDATE$. Here, \tactictoe's proof is arguably smaller, faster and easier to
understand and maintain. Such proofs after an expert review could replace the
their respective original human proofs in the \holfour repository.

>>>>

\section{Case Study}\todo{comment on the case study}
Since the proofs generated by \tactictoe are meant to be part of a \holfour development, it interesting to compare their quality with the original human proofs.
The quality of a proof in \holfour can be measured in terms of length, readability, maintainability and verification speed.
We study these properties in three examples taken from our full-scale experiment.
The time needed by \holfour to check a proof is shown in parentheses.

Example~\ref{ex:cs1} is about proving that greatest common divisors are unique.
The human developer recognizes that it follows easily from two theorems.
Our prover \tactictoe is not able to find that \texttt{DIVIDES\_ANTISYM} is
necessary directly from the shape of the original theorems so it rewrites the
goal then splits the goal into multiple cases until the goal obligations are similar
to \texttt{DIVIDES\_ANTISYM} to be predicted. As expected, \tactictoe's proof
also takes much longer to check.

@@

In Example~\ref{ex:cs2}, we try to prove that for any surjective function $f$
from $s$ to $t$, there exists an injective function $g$ from $t$ to $s$ such
that $f\ o\ g$ is the identity function. The human proof is quite complicated.
In contrast, \tactictoe finds a much smaller proof that expands the
definition of injectivity and surjectivity and calls \metis.
However, the \tactictoe's proof takes much longer to check due to the proof search happening inside \metis.

@@

In Example~\ref{ex:cs3}, we prove a theorem about lists, a domain where \tactictoe excels compared to ATPs.
Given two list $l_1$ and $l_2$ where the length of $l_1$ (noted $p$) is less
than a natural
number $n$, the theorem states updating the $n^{th}$
element of the concatenation of $l_1$ and $l_2$ is the same as
updating the $m^{th}$ element of $l_2$ where $m = n - p$. Again,
\tactictoe's proof is
much more readable starting with applying induction on $l$. It solves the base
case of the induction by rewriting and distinguish cases where $n=0$ or $n>0$
in the inductive hypothesis. It finalizes the proof with a short call to \metis
using the definition of
$LUPDATE$. Here, \tactictoe's proof is arguably smaller, faster and easier to
understand and maintain. Such proofs after an expert review could replace the
their respective original human proofs in the \holfour repository.
